\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{Texas Instruments \hfill Feb 2019 --- Present}}
\subtext{Silicon Product Engineer: Voltage References & Supervisors \hfill Santa Clara, CA}
\begin{zitemize}
\item Worked in international multidisciplinary environment to ensure long term spec performance of shunt references.
\item Developed custom scripting language and parser in Python used to generate I2C and SPI bitstreams for custom IC, enabling the creation of more complex test programs. 
\item Overhauled bench testing setup for custom IC, cutting test times down by a factor of 50, enabling debug of a hold-time violation seen during qualification testing. 
\item Mentored interns and new hires, and led project to improve Python bench automation resources. 
\item Created business case and led PE effort for LM4040 yield improvement, resulting in annual cost savings of \$200k. 
\item Analyzed large set of historical and current data to determine parametric and yield issues in devices. 
\item Deployed test program certification tool on internal web-servers using Python-Flask, Docker, and NGINX.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Texas Instruments (Rotation Program) \hfill Feb 2020 --- Feb 2021}}
\subtext{SerDes Silicon Validation Engineer: FPD-Link \hfill Santa Clara, CA}
\begin{zitemize}
\item Built automation tools to improve test coverage and reduce overall time spent on D-PHY silicon validation.
\item Worked closely with silicon designers to find and fix bugs in ADAS devices to ensure silicon meets datasheet specs.
\item Exponentially reduced test time for system input jitter tolerance test by implementing binary search algorithm. 
\item Designed Python package using multiple-inheritance to streamline device operation, automation, and data collection.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}

\end{document}