\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{RuneLite Open Source Client: ToG Crowdsourcing Plugin \hfill GitHub Open Source Project}}
\subtext{Full Stack Software Engineer 
% \hfill \underline{https://github.com/jcarbelbide/togcrowdsourcing.com}}
\hfill \underline{\href{https://github.com/jcarbelbide/togcrowdsourcing.com}{github.com/jcarbelbide/togcrowdsourcing.com}}}
\begin{zitemize}
\item Developed plugin in Java to crowdsource game data, currently serving over 400 active users, and 12k+ requests per day. 
\item Deployed Go backend on AWS, employing RESTful API design, and utilized NGINX as a reverse proxy to route traffic to different microservices and static web-pages.
\item Placed server behind Cloudflare for metrics monitoring and protection against DDOS and other malicious attacks.
\item Utilized SHA256 hashing algorithm to securely store user data like IP address in SQLite database in order to block repeat POST requests from the same client. 
\item Created Go microservice to monitor RuneScape game servers over JS5 binary socket protocol to detect weekly server reset, and deployed as RESTful API on AWS Linux instance. 
\item Built small, reactive web-application using React to display crowdsourced game data for non-RuneLite and mobile users.
\item Tested server side data verification using Go tests, providing 100\% test coverage on data submissions. 
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Craigslist API \hfill GitHub Personal Project}}
\subtext{Back End Software Engineer 
% \hfill \underline{https://github.com/jcarbelbide/craigslist-api}}
\hfill \underline{\href{https://github.com/jcarbelbide/craigslist-api}{github.com/jcarbelbide/craigslist-api}}}
\begin{zitemize}
\item Developed web-scraper REST API in Python using Beautiful Soup that returns JSON data from Craigslist search. 
\item Dockerized and provided code on GitHub for other users to implement as microservice on Docker machines. 
\item Deployed API on AWS server using NGINX, and designed example web page in React to showcase API.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Pymeasure Open Source Library \hfill GitHub Open Source Project}}
\subtext{Contributor 
% \hfill \underline{https://github.com/pymeasure/pymeasure}}
\hfill \underline{\href{https://github.com/pymeasure/pymeasure}{github.com/pymeasure/pymeasure}}}
\begin{zitemize}
\item Developed and tested Python driver for Thermotron 3800 oven. 
\item Collaborated with community maintainers to ensure implementation follows project best practices. 
\item Provided thorough documentation for implemented GPIB commands. 
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}

\end{document}